---
title: "test1"
output: html_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
```

## Second level header

### Third level header

plain paragraph all on the same line

List of fruits

-   apple
-   kiwi
-   mango
-   coconut

*Nereocystis luetkeana* is a large brown algae endemic to the Eastern Pacific ocean.

Here are some fun facts about *Nereocystis luetkeana*:

1.  common name is bull kelp
2.  it can grow over 100 ft tall
3.  it contains carbon monoxide to help it float
4.  these numbers don't have to be in order but they will knit in order!

## Here is an important header

### and a smaller header

#### a smaller subheader for this equation

$$\sum x_n +3$$ <!--- it is centered with the double $$-->

Table 1. Example table 1.

| Col1 | Col2 | Col3 |
|------|------|------|
| w    | w    | w    |
| w    | w    | w    |
| w    | w    | w    |

Insert a new chunk uding the green square insert chunk icon [@oke2020]. There's also the keyboard shortcut, cmd+opt+i. 

```{r}
x = 2 + 2
y = x*3

```
The green arrow runs the entire chunk. Cmd + return just runs the line you're on (or the whole function you're doing)

```{r}


```
